---
title: Advertisements
author: ''
date: ''
slug: []
categories: []
tags: []
---
```{r libraries, include = FALSE}
# hide
knitr::opts_chunk$set(echo = FALSE)
# libraries
library(tidyverse)
library(ggplot2)
library(blogdown)
library(stargazer)
library(readr)
library(lubridate)
library(rmapshaper)
library(janitor)
library(leaflet)
library(stringr)
library(ggthemes)
library(gridExtra)
library(usdata)
library(ggrepel)
library(usmap)
library(stats)
library(magrittr)
library(dplyr)
library(sf)
library(geojsonio)
library(htmlTable)


incumbent <- read_csv("incumb_dist_1948-2020 (3).csv")
ads <- readRDS("ads_2006_2018 (1).rds")
polls <- read_csv("dist_polls_2018-2022.csv")
```

This week, I explored the effect of political advertisements (from 2006 to 2018) on the Democrat voteshare at the Congressional district level. The specific relationship I will explore is the effect that Democratic advertisement share (the percentage of ads run in the district that were for the Democratic candidate) has on Democratic voteshare.

```{r ads, include = FALSE}
# separate ads data for democrats
ads_dems <- ads %>%
  filter(party == "Democrat") %>%
  group_by(cycle, state, district, st_cd_fips) %>%
  summarize(count = n()) %>%
  rename(year = cycle)

ads_reps <- ads %>% 
  filter(party == "Republican") %>%
  group_by(cycle, state, district, st_cd_fips) %>%
  summarize(count = n()) %>%
  rename(year = cycle)

ads_share <- full_join(ads_dems, ads_reps, by = c("year", "st_cd_fips")) %>%
  mutate(dem_ad_share = count.x/(count.x + count.y) * 100) %>%
  drop_na(dem_ad_share)

dem_results <- incumbent %>% 
  select(year, state, st_cd_fips, DemVotesMajorPercent)
```

```{r models, include = FALSE}
train_data <- full_join(dem_results, ads_share, by = c("year", "st_cd_fips")) %>%
  filter(year < 2018) %>%
  drop_na() %>%
  group_by(state, st_cd_fips) %>%
  filter(n() > 1) %>%
  group_nest() %>%
  mutate(data = map(data, ~unnest(., cols = c())))

models <- train_data %>% 
  mutate(model = map(data, ~lm(DemVotesMajorPercent ~ dem_ad_share, 
                                  data = .x))) %>% 
  select(-data)

model_results <- models %>% 
  mutate(r_squared = map_dbl(model, ~summary(.x)$r.squared), # r-squared values 
         coefficient = map_dbl(model, ~summary(.x)$coefficients[2])) %>%
  select(state, st_cd_fips, r_squared, coefficient)
```

I ran a simple linear regression model between Democratic voteshare and Democratic ad share. The table below shows each district’s linear regression model and its r-squared value and coefficient for Democratic ad share.

```{r table of models}
print(model_results, n = 152)
```

From these model results, I plot the distribution of the coefficients and r-squared values.

```{r coefficient}
# distribution of coefficients of linear regression models
ggplot(data = model_results, mapping = aes(x = coefficient)) +
  geom_histogram(bins = 50, aes(y=..count../sum(..count..)), fill = "lightsteelblue", color = "lightsteelblue4") +
  labs(title = "Distribution of Coefficients of the Linear Regression Models \n(of Democratic Vote Share by Democratic Ad Share)",
       x = "Coefficients",
       y = "Proportion")
```

The above graph is the distribution of the coefficients of the congressional districts available in the 2006-2018 data. Almost all of the coefficients fell in the 0 range.

Because of this, I focus on the center of the graph, which is approximately the -5 to 5 range, by introducing limits.

```{r smaller coefficient}

ggplot(data = model_results, mapping = aes(x = coefficient)) +
  geom_histogram(bins = 50, aes(y=..count../sum(..count..)), fill = "lightsteelblue", color = "lightsteelblue4") +
  labs(title = "Distribution of Coefficients of the Linear Regression Models \n(of Democratic Vote Share by Democratic Ad Share)",
       x = "Coefficients",
       y = "Proportion") +
  xlim(-5, 5)
```

Now, although the distribution is still relatively normal, there are more districts with positive coefficients. This is indicative that there are more districts where there is a positive between Democratic ad share and Democratic voteshare, meaning the greater the Democratic ad share, the greater the Democratic voteshare is.

Next, I examine the distribution of r-squared values.

```{r graph 2}
# distribution of r squared values
ggplot(data = model_results, mapping = aes(x = r_squared)) +
  geom_histogram(bins = 50, aes(y=..count../sum(..count..)), fill = "lightsteelblue", color = "lightsteelblue4") +
  labs(title = "Distribution of R Squared Values  of the Linear Regression Models \n(of Democratic Vote Share by Democratic Ad Share",
       x = "R Squared",
       y = "Proportion")
```

The above graph is the distribution of the r-squared values of the congressional districts available in the 2006-2018 data. Most of the models have an r-squared value of 1. This means that the predicted value was identical to the observed value. This may have been an error, as I tried to filter out districts with only one value to base the prediction on.